The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2024-05-15 MS_ToSubmit/RevisedSupMaterial.Rmd
Add equations

Trophic level

Topological roles

@@

@@

pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

>>>>

#### Betweenness

It is the frequency with which a node is on the shortest path between any other pair of nodes [@Freeman1978]. A node will have high betweenness when it appears on many shortest paths between other pairs of nodes. It is calculated as:

\begin{equation}
BC_i = \sum \frac{g_{vij}} {g_{vj}}
\end{equation}

being $v \neq j, v \neq i, j \neq i$, where $BC_i$ is the betweenness for species $i$; $g_{vj}$ is the number of shortest paths between nodes $v$ and $j$; and $g_{vij}$ is the number of shortest paths which pass through node $i$.

#### Closeness

It is the number of steps required to reach every other node from a given node in the network [@Freeman1978]. It is calculated as the inverse of distances (number of interactions) to all other nodes in the network:

\begin{equation}
C_i = \frac{1} {\sum d_{ij}}
\end{equation}

being $i \neq j$, where $d_{ji}$ is the distance between node $j$ and $i$.

#### Trophic similarity

It measures the trophic overlap based on shared and unique resources (prey) and consumers (predators) of a species. It is calculated as:

\begin{equation}
TS_i = \frac{c} {(a+b+c)}
\end{equation}

where $a$ is the number of prey and predators unique to one node, $b$ is number of prey and predators unique to the other node and $c$ is the number of prey and predators common to both nodes. Where two nodes have exactly the same set of prey and predators, $TS$ = 1; where two nodes have no prey or predators in common, $TS$ = 0.

#### Topological roles

@@

#### Trophic level

@@

pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Link = paste('\\tiny', Link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
